---
title: "Homework 2"
author: "Dorrie Hammond"
date: "9/19/2020"
output: html_document
---
# Honor Pledge
This code is my own work, it was written without consulting a tutor or code written by other students - Dorrie Hammond

## 0.
Places gss.csv dataset into gss dataset.


```{r}
gss <- read.csv("gss.csv") # read gss.csv
```

## 1.

Returns the sum of missing marital files in gss dataset.


```{r}
sum(is.na(gss$marital)) # total of missing marital files
```

## 2.

This finds the percentage of female (about 56%) and male (about 44%) files in gss


```{r}
female <- length(subset(gss$sex,subset = gss$sex == "FEMALE")) / length(gss$sex) * 100
female # percent of female respondents
male <- length(subset(gss$sex,subset = gss$sex == "MALE")) / length(gss$sex) * 100
male # percent of male respondents
```


## 3.

This returns the average number of respondents are the ages 30 to 40 year olds (about 24%).  There has been special care to omit files missing age values.


```{r}
length(na.omit(subset(gss$age, gss$age > 29 & gss$age < 41))) / length(na.omit(gss$age)) * 100 # percent of respondents 30 t0 40
```


## 4.

This returns the average age of respondents from 2008 or 2010 (about 48%).  There has been special care to omit missing values.


```{r}
gss_08_10 <- subset(gss,gss$year == 2008 | gss$year == 2010) # subset of gss files from 2008 or 2010
sum(na.omit(gss_08_10$age)) / length(na.omit(gss_08_10$age)) # average ages from subset
```


