---
title: "Homework 3"
author: '2284917'
date: "9/27/2020"
output: html_document
---

# Honor Pledge
This code is my own work, it was written without consulting a tutor or code written by other students - Dorrie Hammond

## 1.

```{r}
gss <- read.csv("gss.csv") # read gss.csv
summary(gss$year) # summary of gss$year
year2 <- as.factor(gss$year) # gss$year factor
```

## 2.
The new summary of Year2 is different because the first one showed the min,max,mean,etc. of the years, and the second one showed the total number of respondents from every year.  This is because year is considered a numeric column and year2 was defined as a factor column.

```{r}
summary(year2) # summary of gss$year factor
```

## 3.
2006 has the most respondents, with a total number of 4510 respondents.

```{r}
barplot(table(year2)) # barplot to show 2006 with most respondents
sum(year2==2006) # number of respondents from 4510
```


## 4.
The average age of females in 2006 is about 46 years old.


```{r}
mean(gss$age[gss$sex=="FEMALE"|gss$year==2006], na.rm = TRUE) # mean age of female 2006 respondents
```


## 5.

```{r}
gss$income2 <- gss$income
levels(gss$income2)
summary(gss$income2) # summary of income as characters
```

## 6.

```{r}
# create factor of income with new levels
gss$income2<-factor(gss$income, levels=c("1000","2000","12500","17500","22500","25000","3500","4500","5500","6500","7500","9000"))
# define the data in income2 with levels
gss$income2[gss$income=="LT $1000"]<-"1000"
gss$income2[gss$income=="$1000 TO 2999"]<-"2000"
gss$income2[gss$income=="$10000 - 14999"]<-"12500"
gss$income2[gss$income=="$15000 - 19999"]<-"17500"
gss$income2[gss$income=="$20000 - 24999"]<-"22500"
gss$income2[gss$income=="$25000 OR MORE"]<-"25000"
gss$income2[gss$income=="$3000 TO 3999"]<-"3500"
gss$income2[gss$income=="$4000 TO 4999"]<-"4500"
gss$income2[gss$income=="$5000 TO 5999"]<-"5500"
gss$income2[gss$income=="$6000 TO 6999"]<-"6500"
gss$income2[gss$income=="$7000 TO 7999"]<-"7500"
gss$income2[gss$income=="$8000 TO 9999"]<-"9000"
```

## 7.

```{r}
# define NA's
gss$income2[gss$income=="DK"|gss$income2=="REFUSED"]<-NA # NA's
levels(gss$income2)
summary(gss$income2) # prints out summary of new income subset
```

## 8.
Average income for females is about 17700 dollars and for males is 19500 dollars.

```{r}
# income summary as numerics
gss$income2 <- as.numeric(as.character(gss$income2))
summary(gss$income2)
mean(gss$income2[gss$sex=="FEMALE"], na.rm = TRUE) # average female income
mean(gss$income2[gss$sex=="MALE"], na.rm = TRUE) # average male income
```

