---
title: "Homework 4"
author: '2284917'
date: "10/12/2020"
output: html_document
---

# Honor Pledge
This code is my own work, it was written without consulting a tutor or code written by other students - Dorrie Hammond

## 0.

```{r}
library(ggplot2) # load ggplot2 package first
?txhousing # more information about the data set
str(txhousing) # structure of txhousing
```

## 1-3.

The first city I chose to plot is San Antonio, TX. Below is a barplot showing the city's yearly median income from 2000-2015.

```{r}
txhousing_San_Antonio <- subset(txhousing, txhousing$city=="San Antonio")
ggplot(data=txhousing_San_Antonio, aes(x=year, y=median)) +
  geom_bar(stat="identity", fill="steelblue") +
  labs(x="Year",y="Median Income ($)",title="Median Income in San Antonio, TX by Year")+
  theme_bw()
```

## 4.

The second city I chose to plot is Austin, TX. Below is a barplot showing the city's yearly median income from 2000-2015.

```{r}
txhousing_Austin <- subset(txhousing, txhousing$city=="Austin")
ggplot(data=txhousing_Austin, aes(x=year, y=median)) +
  geom_bar(stat="identity", fill="skyblue") +
  labs(x="Year",y="Median Income ($)",title="Median Income in Austin, TX by Year")+
  theme_bw()
```


## 5.

The final plot compares the yearly median incomes in San Antonio and Austin, TX from 2000-2015.

```{r}
txhousing_Two_Cities <- subset(txhousing, txhousing$city=="San Antonio"|txhousing$city=="Austin")
ggplot(data=txhousing_Two_Cities,aes(x=year,y=median,fill=city)) +
  geom_bar(stat="identity",position = position_dodge()) +
  labs(x="Year",y="Median Income ($)",title="Yearly Median Income in Austin vs. San Antonio, TX") +
  scale_fill_brewer(palette="Paired") +
  theme_bw()
```


## 6.

It appears that although both cities share similarly 'shaped' yearly median incomes, Austin's is uniformly greater than San Antonio's every year.  Interestingly, they both took a slight dip in median income in 2011, but then continue to rise in later years. It looks like from 2000-2005 that San Antonio has a steeper increase than Austin, but from 2011-2015 Austin has a steeper increase than San Antonio.

